Current and future constraints on primordial magnetic fields

### 2016-10-27 pmf.tex
a

\begin{figure*}[htb]\centering
\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 5cm 3.8cm}]{pmf_experiments.pdf}
  \caption[Current measurements of CMB B-modes]{
  Current measurements of CMB B-modes. \tbd{Caption to be updated}
      \label{fig:pmf-experiments}
  }
\end{figure*}

>>>>

\begin{figure*}[htb]\centering
\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.5cm 5cm 3.8cm}]{pmf_experiments.pdf}
  \caption[Current measurements of CMB B-modes]{
  Current measurements of CMB B-modes. 
    The black line shows the expected B-mode power in the \planck{} best-fit \lcdm{} cosmology (with the tensor-to-scalar ratio, r set to 0.01). 
    The B-mode measurements used for the limits in this work are denoted with filled circles; data not used has an open circle. 
    The data sets are from POLARBEAR (black; \citet{polarbear}); ACTpol (dark green; \citet{actpol});  BICEP2/Keck Array (red; \citet{bicepkeck}); and SPTpol (purple; \citet{sptpol}). 
      Current B-mode measurements are noise-limited at all angular multipoles; the next generation of experiments is expected to significantly increase the signal-to-noise on the B-mode power spectrum. 
           \label{fig:pmf-experiments}
  }
\end{figure*}
